SMT-Boosted Security Types for Low-Level MPC

### 2025-11-14 toplas26/examples.tex
checkpoint

In Section \ref{section-smt} we gave the example of 3-party additive
sharing for any field $\fieldp{p}$. In Sections \ref{section-ipj} and
\ref{section-metalangty} we discussed the example of YGC input encoding.
Now we consider examples that illustrate the versatility of the
$\TirName{Encode}$ typing rule for confidentiality, the use of
postconditions for correctness, and the use of both pre-~and
postconditions for integrity.

To evaluate our system especially regarding performance, using the
Satisfiability Modulo Fields theory in cvc5 on an Apple M1 processor,
we have verified correctness of additive sharing protocols in fields
up to size $\fieldp{2^{31} - 1}$ (an approximation of 32-bit integers)
which takes $\sim$7ms to compute for 3 parties and not significantly more
than for, e.g., $\fieldp{2}$. We have also verified the semi-homomorphic
encryption properties leveraged in the BDOZ circuit library functions
(Figures \ref{fig-bdozsum} and \ref{fig-bdozmult}) in fields up to
size $\fieldp{2^{31} - 1}$ which take $\sim$8ms for the property used for
the postcondition of the $\ttt{mult}$ gate. This is categorically
better performance than can be achieved using previous brute-force
methods in $\fieldp{2}$ \cite{skalka-near-ppdp24}.

@@

_open(x:string, i1:cid, i2:cid, n:string){ p[x++"n"] := m[x]@i2; m[x++"p"]@i1 = p[x++"n"] + m[x]@i1 }

@@

_open(x:string, i1:cid, i2:cid, n:string){
    p[x++"sn"] := m[x++"s"]@i2;
    p[x++"mn"] := m[x++"m"]@i2;
    assert(p[x++"mn"] = m[x++"k"] + (m["delta"] * p[x++"sn"]))@i1;
    m[x++"p"]@i1 = p[x++"sn"] + m[x]@i1
}

@@

precondition: ( MACed(x) AND MACed(y) AND
                MACed(z++"a") AND MACed(z++"b") AND MACed(z++"c") AND BEAVERTRIP(z) )
mult(z : string, x : string, y : string) {
    secopen(z++"d", x, z++"a"); secopen(z++"e", y, z++"b"); _mult(z,y,1); _mult(z,y,2);
}
postcondition: ( RECON(z) == RECON(x) * RECON(y) )

\end{verbatimtab}
\end{fpfig}

>>>>

In Section \ref{section-smt} we gave the example of 3-party additive
sharing for any field $\fieldp{p}$, in Section \ref{section-sty} we
discussed the example of YGC input encoding, and in Sections
\ref{section-metalang} and \ref{section-metaty} we presented and
discussed the example of gates in the GMW protocol for binary
circuits. In this section we present an extended example of arithmetic
circuits with multiplication gates defined using Beaver triples
\cite{evans2018pragmatic}. We first define a compositional gate
library in $\metaprot$ with correctness conditions defined using the
Hoare logic developed in Section \ref{section-metalang}, along with a
small example circuit.  Then we will extend the library with type
annotations illustrating the use of share types developed in
Sections \ref{section-sty} and \ref{section-metaty} to enforce
confidentiality properties. Last, we will extend the base library
with additional pre and postcondition annotations to enforce
integrity properties supported by BDOZ/SPDZ style MACs
\cite{SPDZ1,SPDZ2,BDOZ,10.1007/978-3-030-68869-1_3}.

To evaluate our system especially regarding performance, using the
Satisfiability Modulo Fields theory in cvc5 on an Apple M1 processor,
we have verified correctness of these arithmetic gate libraries and
circuit in fields up to size $\fieldp{2^{31} - 1}$ (an approximation
of 32-bit integers) which takes $\sim$7ms to compute for 3 parties and
not significantly more than for, e.g., $\fieldp{2}$. We have also
verified the semi-homomorphic encryption properties leveraged in the
BDOZ circuit library functions in fields up to size $\fieldp{2^{31} -
  1}$ which take $\sim$8ms for the property used for the postcondition
of the $\ttt{mult}$ gate. This is categorically better performance
than can be achieved using previous brute-force methods in
$\fieldp{2}$ \cite{skalka-near-ppdp24}.

\subsection{Arithmetic Circuits with Beaver Triples}

@@

_open(x:string, i1:cid, i2:cid, n:string){ p[x++"n"] := m[x]@i2; m[x++"p"]@i1 := p[x++"n"] + m[x]@i1 }

@@

_open(x:string, i1:cid, i2:cid, n:string){
    p[x++"sn"] := m[x++"s"]@i2;
    p[x++"mn"] := m[x++"m"]@i2;
    assert(p[x++"mn"] = m[x++"k"] + (m["delta"] * p[x++"sn"]))@i1;
    m[x++"p"]@i1 := p[x++"sn"] + m[x]@i1
}

@@

precondition: ( MACed(x) AND MACed(y) AND
                MACed(z++"a") AND MACed(z++"b") AND MACed(z++"c") AND BEAVERTRIP(z) )
mult(z : string, x : string, y : string) {
    secopen(z++"d", x, z++"a"); secopen(z++"e", y, z++"b"); _mult(z,y,1); _mult(z,y,2);
}
postcondition: ( RECON(z) == RECON(x) * RECON(y) )
\end{verbatimtab}
\end{fpfig}
